\sysfull

### 2017-08-12 paper/evaluation.tex
fixed typo
pagefault figs
eval text

We measured compile time for \sys's compiler's automatic task generation for
each application\footnote{We could not compile the dft application since LLVM
inserts mathematical built-in functions (i.e. \texttt{\_\_muldf3},
\texttt{\_\_floatsidf}, \texttt{\_\_adddf3}) whose implementation were not
provided by the LLVM MSP430 back-end.}. We compiled the applications on a
4-core virtual machine with 1\,GB of memory running Arch Linux on an Intel Core
i5-6200U at 2.30\,GHz. We collected results using the Linux system time
collected in seconds. Most of the compile time was spent computing pointer
alias analysis, while calculating the possible live ranges of variables.
Applications such as RSA that have a larger code size and that manipulate more
variables have a longer compilation time, due to a larger search space for
pointer aliasing. Nonetheless, the compile time is orders of magnitude shorter
than manually defining tasks, which requires hours of programmer time. The
characterization of \sys's compiler suggests that the \sys compiler enables
simpler task-based intermittent programmer for \sys.

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/pagSizeOverhead}
	\caption{Normalized page size overhead and page faults per benchmark.}
	\label{fig:IPOSPerformance}
	\label{fig:page_size}
\end{figure}

Figure~\ref{fig:page_size} presents the result on the effect of page swap size on the execution time of the programs executed by \sys. Overhead has been measured in the MCU clock cycles with values provided by TI CCS. Result has been normalized per benchmark: for the overhead results---to the minimum obtained value and for page faults---to the third measured maximum value. A subset of applications has been selected for evaluation. Additionally, page faults have been measured. The result show clearly a bathtub-shape bar plot for each application, demonstrating that for each application there is always a page size that minimizes \emph{both} execution time and page swaps. For all applications (except for Sort) this value equals roughly to 64 bytes. The shape of each figure can be explained as follows. For small page sizes (<64) the execution time is dominated by the \emph{frequency} of page swaps. On the other hand, in the opposite case the execution time is dominated by the time of swapping of one large page from SRAM to FRAM. Another interesting observation is the non-symmetric shape of each bar plot. This is due the size of data manipulated by the program: minimum point of overhead equals roughly to the size of the variables manipulated by each benchmark. Worth noting is also large discrepancy between minimum and maximum overhead for each benchmark (e.g. for Cuckoo 8 (at 16 bytes) to 1 (at 64 bytes), BC: 1 (at 16 bytes) to $\approx$2 (at 1024 bytes)).

>>>>

We measured compile time for \sys's compiler's automatic task generation for
each application\footnote{We could not compile the dft application since LLVM
inserts mathematical built-in functions (i.e. \texttt{\_\_muldf3},
\texttt{\_\_floatsidf}, \texttt{\_\_adddf3}) whose implementation were not
provided by the LLVM MSP430 back-end.}. We compiled the applications on a
4-core virtual machine with 1\,GB of memory running Arch Linux on an Intel Core
i5-6200U at 2.30\,GHz. We collected results using the Linux system time
collected in seconds. Most of the compile time was spent computing pointer
alias analysis, while calculating the possible live ranges of variables.
Applications such as RSA that have a larger code size and that manipulate more
variables have a longer compilation time, due to a larger search space for
pointer aliasing. Nonetheless, the compile time is orders of magnitude shorter
than manually defining tasks, which requires hours of programmer time. The
characterization of \sys's compiler suggests that the \sys compiler enables
simpler task-based intermittent programming for \sys.

@@

We evaluated the effect that paging with different page sizes has on \sys's
performance and we show data in Figure~\ref{fig:page_size}. We show two plots:
the top plot shows the run time performance normalized to the best
per-application performance, using pages of different sizes in \sys, indicated
with the labels on top of each cem bar; the bottom plot shows the number of
page faults for the same set of executions normalized to the maximum of each
set.
%
We measured performance as MCU clock cycles using values read out by TI's CCS
IDE. 
%
The results show a clear ``bathtub curve'' in the performance of each
application, as the number of page faults varies. The data show that across
application there is a page size that minimizes \emph{both} execution time.  We
observe that the page size is not the same for each application, although 64
byte pages perform well for all applications except sort. The increased rate of
page faults is responsible for the overhead with small page sizes; smaller
pages require accessing more different pages, leading to higher paging costs.
With larger page sizes, the overhead is higher than with moderate pages, too.
The explanation for these higher overheads is that large pages have a higher
commit cost. Even if an application accesses few memory locations, \sys pages
data at full page size, degrading performance by sometimes paging in and out
unnecessary data.  The data reveal a reasonable default page size of 64 bytes
and when developing an application, a developer should consider varying the
page size to moderate poor performance.

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/pagSizeOverhead}
	\includegraphics[width=\columnwidth]{figures/pagefault}
	\caption{\sys's page size affects overhead and page fault count.}
	\label{fig:IPOSPerformance}
	\label{fig:page_size}
\end{figure}
